Wordstack and outline of the manuscript

### 2021-10-12 paper/method_figure.Rmd
Update introduction and results

source(mypath("R", "misc.R"))
source_dir(mypath("R"))
theme_set(theme_cowplot())
```

@@

@@

save_plot(
  "figures/decreasing_biomass_network.png", g,
  nrow = 3,
  ncol = 4,
  base_height = 4,
  base_width = 4)

@@

save_plot(
  "figures/increasing_biomass_network.png", g2,
  nrow = 4,
  ncol = 4,
  base_height = 4,
  base_width = 4)
```

@@

save_plot(
  "figures/decreasing_biomass.png", tps_bm_dec,
  nrow = 1,
  ncol = 1,
  base_height = 4,
  base_width = 7)

@@

save_plot(
  "figures/increasing_biomass.png", tps_bm_inc,
  nrow = 1,
  ncol = 1,
  base_height = 4,
  base_width = 7)
```

@@

plot_temporal_variable_lm <- function(
  .df = full_data2,
  var = "ct_ff",
  st = 15818) {
  .df %>%
    filter(station %in% st) %>%
    mutate(
      year = ymd(year, truncated = 2L),
      station = str_replace_all(station, setNames(names(st), st))
      ) %>%
    ggplot(aes_string(x = "year", y = var)) +
    geom_point() +
    geom_smooth(aes(group = station), method = "lm", formula = y ~ x,
      size = 1, se = FALSE, color = "black") +
    labs(x = "Year", y = str_replace_all(var, var_replacement()))

@@

```{r}
loadd(map_st)

test_fig_mat_met <- plot_grid(
  map_st,
  plot_grid( plot_grid(tps_bm_dec, tps_bm_inc)),
  plot_grid(plotlist = tps_dec_inc),
  nrow = 3
)
save_plot(
  test_fig_mat_met,
  base_height = 7,
  base_asp = 1.618,
  file = get_mypath("figures", "matmet.png")
)
```

>>>>

source(mypath("R", "misc.R"))
source(mypath("R", "variable_shortcut.R"))
source_dir(mypath("R"))
theme_set(theme_cowplot())
```

@@

```{r}
myload(metaweb_analysis, dir = get_mypath("data"), envir = environment())

my_species_color <- set_color_species(
  node_list = colnames(metaweb_analysis$metaweb),
  resource_list = metaweb_analysis$resource,
  col_resource = NULL
)
```

@@

save_plot(
  get_mypath("figures/decreasing_biomass_network.png"),
  g,
  nrow = 3,
  ncol = 4,
  base_height = 4,
  base_width = 4)

@@

save_plot(
  get_mypath("figures/increasing_biomass_network.png"), g2,
  nrow = 4,
  ncol = 4,
  base_height = 4,
  base_width = 4)
```

@@

save_plot(
  get_mypath("figures/decreasing_biomass.png"), tps_bm_dec,
  nrow = 1,
  ncol = 1,
  base_height = 4,
  base_width = 7)

@@

save_plot(
  get_mypath("figures/increasing_biomass.png"), tps_bm_inc,
  nrow = 1,
  ncol = 1,
  base_height = 4,
  base_width = 7)
```

@@

plot_temporal_variable_lm <- function(
  .df = full_data2,
  var = "ct_ff",
  st = 15818) {
  tex <- .df %>%
    filter(station %in% st) %>%
    mutate(
      year = ymd(year, truncated = 2L)
    )

    if(!is.null(names(st))) {
      tex %<>%
        mutate(station = str_replace_all(station, setNames(names(st), st)))
    }

    tex %>%
      ggplot(aes_string(x = "year", y = var)) +
      geom_point() +
      geom_smooth(aes(group = station), method = "lm", formula = y ~ x,
        size = 1, se = FALSE, color = "black") +
      labs(x = "Year", y = str_replace_all(var, var_replacement()))

@@

## plot map

```{r}
loadd(map_st)
save_plot(map_st,
  base_height = 11,
  base_asp = 1.618,
  file = get_mypath("figures", "map_st.png")
)
```

```{r}
test_fig_mat_met <- plot_grid(
  map_st,
  plot_grid( plot_grid(tps_bm_dec, tps_bm_inc)),
  plot_grid(plotlist = tps_dec_inc),
  nrow = 3
)
save_plot(
  test_fig_mat_met,
  base_height = 12,
  base_asp = 1.618,
  file = get_mypath("figures", "matmet.png")
)
```

# New figure

```{r}
# get a station that represents the results 
st_var_shape <- rigal_classification %>%
  unnest(classif) %>%
  filter(variable %in% c(get_com_str_var(), "log_bm_std")) %>%
  select(station, variable, direction)  %>%
  pivot_wider(names_from = variable, values_from = direction) 
dec_representative <- st_var_shape %>%
  filter(log_bm_std == "decrease", ct_ff == "decrease", w_trph_lvl_avg == "decrease") 
```

```{r}
tes <- map(dec_representative$station, ~plot_dyn_web(
    com = community_metrics,
    sem_df = NULL,
    station = .x,
#    .log = TRUE,
    stacked = TRUE, 
    color_species = NULL 
    ))
plot_grid(plotlist = tes)
```
```{r}
st_decreasing <- dec_representative$station[3]

p_dec_log_bm <- tes[[3]] +
  labs(color = "Species", fill = "Species") +
  theme(legend.position = "bottom")

save_plot(
  get_mypath("figures/p_dec_log_bm.png"),
  p_dec_log_bm,
  nrow = 1,
  ncol = 1,
  base_asp = 1.618,
  base_width = 7)
```
```{r}
tps_dec_inc <- map(c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "piel_bm"),
  ~plot_temporal_variable_lm(st = st_decreasing, var = .x)
)
save_plot(
  filename = get_mypath("figures/net_str_dec_bm.png"),
  plot_grid(plotlist = tps_dec_inc),
  nrow = 2, ncol = 2,
  base_asp = 1.618,
  base_width = 5
)
```
```{r temporal foodwebs}

p <- get_network_temporal_plot(
  net_list = network_analysis,
  station = st_decreasing,
  selected_years = c(1996, 2006, 2016),
  node_color = my_species_color, scale_node_size = 0.027,
  par_options = par(mar = c(0,0,0,0)),
  log_abun = TRUE
)
g <- plot_grid(plotlist = map(p, ggdraw), ncol = 3)

save_plot(
  get_mypath("figures/decreasing_biomass_network.pdf"),
  g,
  ncol = 3,
  base_asp = 1.618,
  base_width = 7)
```

## plot map

```{r}
loadd(map_st)
save_plot(map_st,
  base_height = 11,
  base_asp = 1.618,
  file = get_mypath("figures", "map_st.png")
)
```

```{r}

test_fig_mat_met <- plot_grid(
  map_st,
  plot_grid( plot_grid(tps_bm_dec, tps_bm_inc)),
  plot_grid(plotlist = tps_dec_inc),
  nrow = 3
)
save_plot(
  test_fig_mat_met,
  base_height = 12,
  base_asp = 1.618,
  file = get_mypath("figures", "matmet.png")
)
```

```{r}
test_mat_met <- plot_grid(
  plot_grid(map_st, p_dec_log_bm, ncol = 2),
  plot_grid(plot_grid(plotlist = tps_dec_inc), g, ncol = 2),
  nrow = 2
)
save_plot(
  get_mypath("figures/test_mat_met.png"),
  test_mat_met,
  base_asp = .5,
  base_width = 9
)
```
